---
title: "Vector_ForPublication"
author: "Cori"
date: "3/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr) 
library(VecStatGraphs2D) # generated vector plots
library(plotrix)
library(REdaS)
library(maps)
library(rworldmap)
library(rworldxtra)
library(rgdal)
library(tRophicPosition)
```

###############################
## BLACK AND ARMBRUSTER 2020 ##
###############################

###### BaSIVA ###### 
Download data
```{r}
si.data=read.csv('Raw_data.txt', header = T, sep="\t")
```

Standardize Data
```{r}
# Find mean of basal resources
baseline=subset(si.data, subset = Detailed.Source %in% c("green filamentous algae", "green algae", "algae", "moss", "green algae/periphyton"))

baseline.means=data.frame(baseline$Location, baseline$d15N, baseline$d13C)
baseline.means=aggregate(baseline.means, list(baseline.means$baseline.Location), mean)
row.names(baseline.means)=baseline.means$Group.1 #data clean up
baseline.means$Group.1=NULL #data clean up
baseline.means$baseline.Location=NULL #data clean up

# Isolate consumers from basal resources and remove NA
consumers=subset(si.data, FG == "fish") 
consumers=na.omit(consumers)

# Subtract basal mean from indiviual at each location 
PER13=subset(consumers, Location == "13")
PER13$standardized.d15N=PER13$d15N-baseline.means[1,1]
PER13$standardized.d13C=PER13$d13C-baseline.means[1,2]

PER15=subset(consumers, Location == "15")
PER15$standardized.d15N=PER15$d15N-baseline.means[2,1]
PER15$standardized.d13C=PER15$d13C-baseline.means[2,2]

PER17=subset(consumers, Location == "17")
PER17$standardized.d15N=PER17$d15N-baseline.means[3,1]
PER17$standardized.d13C=PER17$d13C-baseline.means[3,2]

PER19=subset(consumers, Location == "19")
PER19$standardized.d15N=PER19$d15N-baseline.means[4,1]
PER19$standardized.d13C=PER19$d13C-baseline.means[4,2]

# Check that baselines are now set to 0 (sanity check)
baseline.means[1,1] - baseline.means[1,1]
baseline.means[1,2] - baseline.means[1,2]
baseline.means[2,1] - baseline.means[2,1]
baseline.means[2,2] - baseline.means[2,2]
baseline.means[3,1] - baseline.means[3,1]
baseline.means[3,2] - baseline.means[3,2]
baseline.means[4,1] - baseline.means[4,1]
baseline.means[4,2] - baseline.means[4,2]

# Combine assemblages together
consumers.vectors=rbind(PER13,PER15,PER17,PER19)

write.csv(consumers.vectors,file = "baselines.txt")
```

Vector Analysis
```{r}
# Export standardized data to complete vector analysis
vector.out=consumers.vectors[,10:11]
write.table(vector.out, file="vectors.txt", sep="\t", col.names = F, row.names = F) ### DO NOT CHANGE THIS FILE BEFORE NEXT STEP! Data must say in order so it can be combine with all data
```

Azimuth stats
```{r}
## Read vectors for all consumers
vector.in=LoadData("vectors.txt", Type = 2)
consumers.vectors$Azimuth=vector.in[,2]
consumers.vectors$Module=vector.in[,1]

# Calculate radians for vector plots
consumers.vectors$radians=deg2rad(consumers.vectors$Azimuth)

# Remove unknown species from data set
final.vectors=subset(consumers.vectors, Source != "AUF-10519")
final.vectors=subset(final.vectors, Source != "AUF-10630")
final.vectors=subset(final.vectors, Source != "AUSI-10012_AUF-10498 (CHECK)")
final.means=aggregate(final.vectors, list(final.vectors$Source), mean)

#write.csv(file = "final.vectors.txt",final.vectors)

## Vector stats for all specimens
AllAzimuthStatistics(final.vectors$Azimuth)
AllModuleStatistics(final.vectors$Module)

## Vector stats for each species
Ancistrus=subset(final.vectors,Source == "Ancistrus sp.")
AllAzimuthStatistics(Ancistrus$Azimuth)
AllModuleStatistics(Ancistrus$Module)

Astroblepus=subset(final.vectors,Source == "Astroblepus sp.")
AllAzimuthStatistics(Astroblepus$Azimuth)
AllModuleStatistics(Astroblepus$Module)

Chaetostoma_brevae=subset(final.vectors,Source == "Chaetostoma breve")
AllAzimuthStatistics(Chaetostoma_brevae$Azimuth)
AllModuleStatistics(Chaetostoma_brevae$Module)

Chaetostoma_microps=subset(final.vectors,Source == "Chaetostoma microps")
AllAzimuthStatistics(Chaetostoma_microps$Azimuth)
AllModuleStatistics(Chaetostoma_microps$Module)

Cordylancistrus=subset(final.vectors,Source == "Cordylancistrus sp.")
AllAzimuthStatistics(Cordylancistrus$Azimuth)
AllModuleStatistics(Cordylancistrus$Module)

Hypostomus_niceforoi=subset(final.vectors,Source == "Hypostomus niceforoi")
AllAzimuthStatistics(Hypostomus_niceforoi$Azimuth)
AllModuleStatistics(Hypostomus_niceforoi$Module)

Lamontichthys=subset(final.vectors,Source == "Lamontichthys sp.")
AllAzimuthStatistics(Lamontichthys$Azimuth)
AllModuleStatistics(Lamontichthys$Module)

Spatoloricarid=subset(final.vectors,Source == "Spatoloricarid sp.")
AllAzimuthStatistics(Spatoloricarid$Azimuth)
AllModuleStatistics(Spatoloricarid$Module)
```

*FIGURE 2: Standardization Biplot
```{r}
# isolate by location
PER13=subset(final.vectors, Location == "13")
PER15=subset(final.vectors, Location == "15")
PER17=subset(final.vectors, Location == "17")
PER19=subset(final.vectors, Location == "19")

# set color pal
colblind_pal=c("#000000", "#004949", "#009292", "#ff6db6", "#ffb677", "#490092", "#006ddb", "#b66dff", "#b6dbff", "#920000", "#924900", "#dbd100", "#24ff24", "#ffff6d", "#6db6ff")
names(colblind_pal)=(c("Ancistrus sp.","Astroblepus sp.","Chaetostoma breve","Chaetostoma microps","Cordylancistrus sp.","Hypostomus niceforoi","Lamontichthys sp.","Spatoloricarid sp."))
colblind_pal=colblind_pal[match(final.vectors$Source, names(colblind_pal))]

#Generate figure
pdf(file = "Figure1.1.pdf", width = 6, height = 10)
par(mfrow=c(2,1))
#part a.
plot(PER13$d15N,PER13$d13C,col="#004949", pch=0, ylim = c(-30,13), xlim = c(0,12), xlab = "d15N", ylab = "d13C")
points(PER13$standardized.d15N,PER13$standardized.d13C, col="#004949", pch=15) #solid square
points(PER15$d15N, PER15$d13C, col="#ff6db6", pch=0)
points(PER15$standardized.d15N,PER15$standardized.d13C, col="#ff6db6", pch=15) #solid square
points(PER17$d15N, PER17$d13C, col="#b66dff", pch=0)
points(PER17$standardized.d15N,PER17$standardized.d13C, col="#b66dff", pch=15) #solid square
points(PER19$d15N, PER19$d13C, col="#006ddb", pch=0)
points(PER19$standardized.d15N,PER19$standardized.d13C, col="#006ddb", pch=15) #solid square

points(0,0, col="black", pch=19, cex=2) 
points(baseline.means[1,1], baseline.means[1,2], col="#004949", pch=1, cex=2)
points(baseline.means[2,1], baseline.means[2,2], col="#ff6db6", pch=1, cex=2)
points(baseline.means[3,1], baseline.means[3,2], col="#b66dff", pch=1, cex=2)
points(baseline.means[4,1], baseline.means[4,2], col="#006ddb", pch=1, cex=2)

arrows(baseline.means[1,1], baseline.means[1,2], 0, 0, col="#004949", lty=1, lwd=3, length = .1)
arrows(baseline.means[3,1], baseline.means[3,2], 0, 0, col="#b66dff", lty=1, lwd=3,length = .1)
arrows(baseline.means[2,1], baseline.means[2,2], 0, 0, col="#ff6db6", lty=1, lwd=3,length = .1)
arrows(baseline.means[4,1], baseline.means[4,2], 0, 0, col="#006ddb", lty=1, lwd=3,length = .1)
arrows(mean(PER13$d15N),mean(PER13$d13C),mean(PER13$standardized.d15N),mean(PER13$standardized.d13C), lty=1, col = "#004949", lwd=3,length = .1)
arrows(mean(PER17$d15N),mean(PER17$d13C),mean(PER17$standardized.d15N),mean(PER17$standardized.d13C),col = "#b66dff", lty=1, lwd=3,length = .1)
arrows(mean(PER15$d15N),mean(PER15$d13C),mean(PER15$standardized.d15N),mean(PER15$standardized.d13C),col = "#ff6db6", lty=1, lwd=3,length = .1)
arrows(mean(PER19$d15N),mean(PER19$d13C),mean(PER19$standardized.d15N),mean(PER19$standardized.d13C),col = "#006ddb", lty=1, lwd=3,length = .1)

#part b.
plot(0,0, col="black", pch=19, cex=2, ylim = c(-10,10), xlim = c(0,10), xlab = "d15N", ylab = "d13C")
arrows(0,0,final.vectors$standardized.d15N,final.vectors$standardized.d13C, lty=1, col = "black", lwd=1,length = .1)
points(final.vectors$standardized.d15N, final.vectors$standardized.d13C, col=colblind_pal, pch=15)
dev.off()

```

```{r}
#Generate figure
pdf(file = "Figure1.1.pdf", width = 6, height = 10)
par(mfrow=c(2,1))
#part a.
plot(PER13$d13C,PER13$d15N,col="#004949", pch=0, ylim = c(0,12), xlim = c(-30,13), xlab = "d13C", ylab = "d15N")
points(PER13$standardized.d13C,PER13$standardized.d15N, col="#004949", pch=15) #solid square
points(PER15$d13C, PER15$d15N, col="#ff6db6", pch=0)
points(PER15$standardized.d13C,PER15$standardized.d15N, col="#ff6db6", pch=15) #solid square
points(PER17$d13C, PER17$d15N, col="#b66dff", pch=0)
points(PER17$standardized.d13C,PER17$standardized.d15N, col="#b66dff", pch=15) #solid square
points(PER19$d13C, PER19$d15N, col="#006ddb", pch=0)
points(PER19$standardized.d13C,PER19$standardized.d15N, col="#006ddb", pch=15) #solid square

points(0,0, col="black", pch=19, cex=2) 
points(baseline.means[1,2], baseline.means[1,1], col="#004949", pch=1, cex=2)
points(baseline.means[2,2], baseline.means[2,1], col="#ff6db6", pch=1, cex=2)
points(baseline.means[3,2], baseline.means[3,1], col="#b66dff", pch=1, cex=2)
points(baseline.means[4,2], baseline.means[4,1], col="#006ddb", pch=1, cex=2)

arrows(baseline.means[1,2], baseline.means[1,1], 0, 0, col="#004949", lty=1, lwd=3, length = .1)
arrows(baseline.means[3,2], baseline.means[3,1], 0, 0, col="#b66dff", lty=1, lwd=3,length = .1)
arrows(baseline.means[2,2], baseline.means[2,1], 0, 0, col="#ff6db6", lty=1, lwd=3,length = .1)
arrows(baseline.means[4,2], baseline.means[4,1], 0, 0, col="#006ddb", lty=1, lwd=3,length = .1)
arrows(mean(PER13$d13C),mean(PER13$d15N),mean(PER13$standardized.d13C),mean(PER13$standardized.d15N), lty=1, col = "#004949", lwd=3,length = .1)
arrows(mean(PER17$d13C),mean(PER17$d15N),mean(PER17$standardized.d13C),mean(PER17$standardized.d15N),col = "#b66dff", lty=1, lwd=3,length = .1)
arrows(mean(PER15$d13C),mean(PER15$d15N),mean(PER15$standardized.d13C),mean(PER15$standardized.d15N),col = "#ff6db6", lty=1, lwd=3,length = .1)
arrows(mean(PER19$d13C),mean(PER19$d15N),mean(PER19$standardized.d13C),mean(PER19$standardized.d15N),col = "#006ddb", lty=1, lwd=3,length = .1)

#part b.
plot(0,0, col="black", pch=19, cex=2, ylim = c(0,10), xlim =c(-10,10) , xlab = "d13C", ylab = "d15N")
arrows(0,0,final.vectors$standardized.d13C,final.vectors$standardized.d15N, lty=1, col = "black", lwd=1,length = .1)
points(final.vectors$standardized.d13C, final.vectors$standardized.d15N, col=colblind_pal, pch=15)
dev.off()

```

*FIGURE 4: Vector plots by species
```{r}
#directionlabels <- c("C rich", "N rich", "C poor", "N poor")
par(cex.axis=0.25)
par(cex.lab=0.25)

pdf(file = "Figure_species.pdf", width = 20, height = 10)
par(mfrow=c(2,4))
radial.plot(c(0, Ancistrus$Module), 
            c(0, Ancistrus$radians), 
            lwd=1, line.col="#000000",
            labels=NULL,
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=TRUE, #put the concentric circle labels going down
            show.radial.grid=TRUE
)
radial.plot(c(0, Astroblepus$Module), 
            c(0, Astroblepus$radians), 
            lwd=1, line.col="#004949",
            labels=NULL,
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, Chaetostoma_brevae$Module), 
            c(0, Chaetostoma_brevae$radians), 
            lwd=1, line.col="#009292",
            labels=NULL,
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, Chaetostoma_microps$Module), 
            c(0, Chaetostoma_microps$radians), 
            lwd=1, line.col="#ff6db6",
            labels=NULL,
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, Cordylancistrus$Module), 
            c(0, Cordylancistrus$radians), 
            lwd=1, line.col="#ffb677",
            labels=NULL,
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, Hypostomus_niceforoi$Module), 
            c(0, Hypostomus_niceforoi$radians), 
            lwd=1, line.col="#490092",
            labels=NULL,
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, Lamontichthys$Module), 
            c(0, Lamontichthys$radians), 
            lwd=1, line.col="#006ddb",
            labels=NULL,
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, Spatoloricarid$Module), 
            c(0, Spatoloricarid$radians), 
            lwd=1, line.col="#b66dff",
            labels=NULL,
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
dev.off()

#Plot means of each species
par(cex.axis=0.25)
par(cex.lab=0.25)

pdf(file = "Figure_means.pdf", width = 20, height = 10)
par(mfrow=c(2,4))
radial.plot(c(0, mean(Ancistrus$Module)), 
            c(0, mean(Ancistrus$radians)), 
            lwd=6, line.col="#000000",
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, mean(Astroblepus$Module)), 
            c(0, mean(Astroblepus$radians)), 
            lwd=6, line.col="#004949",
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, mean(Chaetostoma_brevae$Module)), 
            c(0, mean(Chaetostoma_brevae$radians)), 
            lwd=6, line.col="#009292",
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, mean(Chaetostoma_microps$Module)), 
            c(0, mean(Chaetostoma_microps$radians)), 
            lwd=6, line.col="#ff6db6",
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, mean(Cordylancistrus$Module)), 
            c(0, mean(Cordylancistrus$radians)), 
            lwd=6, line.col="#ffb677",
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, mean(Hypostomus_niceforoi$Module)), 
            c(0, mean(Hypostomus_niceforoi$radians)), 
            lwd=6, line.col="#490092",
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, mean(Lamontichthys$Module)), 
            c(0, mean(Lamontichthys$radians)), 
            lwd=6, line.col="#006ddb",
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, mean(Spatoloricarid$Module)), 
            c(0, mean(Spatoloricarid$radians)), 
            lwd=6, line.col="#b66dff",
            radial.lim = c(0,10), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
dev.off()
```


##############################
## LUJAN ET AL. 2012 METHOD ##
##############################

###### ACSIVA ###### 
Vector means
```{r}
# Find means for entire comsumer community
vector.means=data.frame(consumers$Location, consumers$d15N, consumers$d13C)
vector.means=aggregate(vector.means, list(vector.means$consumers.Location), mean)
row.names(vector.means)=vector.means$Group.1
vector.means$Group.1=NULL
vector.means$consumers.Location=NULL

# Find vector of each individual in assemblage
PER13$ACSIVA.d15N=PER13$d15N-vector.means[1,1]
PER13$ACSIVA.d13C=PER13$d13C-vector.means[1,2]

PER15$ACSIVA.d15N=PER15$d15N-vector.means[2,1]
PER15$ACSIVA.d13C=PER15$d13C-vector.means[2,2]

PER17$ACSIVA.d15N=PER17$d15N-vector.means[4,1]
PER17$ACSIVA.d13C=PER17$d13C-vector.means[4,2]

PER19$ACSIVA.d15N=PER19$d15N-vector.means[5,1]
PER19$ACSIVA.d13C=PER19$d13C-vector.means[5,2]

# Combine assemblages
ACSIVA.vectors=rbind(PER13,PER15,PER17,PER19)
```

Vector Analysis
```{r}
# Export standardized data to complete vector analysis
ACSIVA.vector.out=ACSIVA.vectors[,15:16]
write.table(ACSIVA.vector.out, file="ACSIVA.vectors.txt", sep="\t", col.names = F, row.names = F) ### DO NOT CHANGE THIS FILE BEFORE NEXT STEP! Data must say in order so it can be combine with all data
```

Azimuth stats
```{r}
## Read vectors for all consumers
ACSIVA.vector.in=LoadData("ACSIVA.vectors.txt", Type = 2)
ACSIVA.vectors$Azimuth=ACSIVA.vector.in[,2]
ACSIVA.vectors$Module=ACSIVA.vector.in[,1]

# Calculate radians for vector plots
ACSIVA.vectors$radians=deg2rad(ACSIVA.vectors$Azimuth)

# Remove unknown species from data set
finalACSIVA.vectors=subset(ACSIVA.vectors, Source != "AUF-10519")
finalACSIVA.vectors=subset(finalACSIVA.vectors, Source != "AUF-10630")
finalACSIVA.vectors=subset(finalACSIVA.vectors, Source != "AUSI-10012_AUF-10498 (CHECK)")
finalACSIVA.means=aggregate(finalACSIVA.vectors, list(finalACSIVA.vectors$Source), mean)

## Vector stats for all specimens
AllAzimuthStatistics(finalACSIVA.vectors$Azimuth)
AllModuleStatistics(finalACSIVA.vectors$Module)

## Vector stats for each species
Ancistrus.ACSIVA=subset(finalACSIVA.vectors,Source == "Ancistrus sp.")
AllAzimuthStatistics(Ancistrus.ACSIVA$Azimuth)
AllModuleStatistics(Ancistrus.ACSIVA$Module)

Astroblepus.ACSIVA=subset(finalACSIVA.vectors,Source == "Astroblepus sp.")
AllAzimuthStatistics(Astroblepus.ACSIVA$Azimuth)
AllModuleStatistics(Astroblepus.ACSIVA$Module)

Chaetostoma_brevae.ACSIVA=subset(finalACSIVA.vectors,Source == "Chaetostoma breve")
AllAzimuthStatistics(Chaetostoma_brevae.ACSIVA$Azimuth)
AllModuleStatistics(Chaetostoma_brevae.ACSIVA$Module)

Chaetostoma_microps.ACSIVA=subset(finalACSIVA.vectors,Source == "Chaetostoma microps")
AllAzimuthStatistics(Chaetostoma_microps.ACSIVA$Azimuth)
AllModuleStatistics(Chaetostoma_microps.ACSIVA$Module)

Cordylancistrus.ACSIVA=subset(finalACSIVA.vectors,Source == "Cordylancistrus sp.")
AllAzimuthStatistics(Cordylancistrus.ACSIVA$Azimuth)
AllModuleStatistics(Cordylancistrus.ACSIVA$Module)

Hypostomus_niceforoi.ACSIVA=subset(finalACSIVA.vectors,Source == "Hypostomus niceforoi")
AllAzimuthStatistics(Hypostomus_niceforoi.ACSIVA$Azimuth)
AllModuleStatistics(Hypostomus_niceforoi.ACSIVA$Module)

Lamontichthys.ACSIVA=subset(finalACSIVA.vectors,Source == "Lamontichthys sp.")
AllAzimuthStatistics(Lamontichthys.ACSIVA$Azimuth)
AllModuleStatistics(Lamontichthys.ACSIVA$Module)

Spatoloricarid.ACSIVA=subset(finalACSIVA.vectors,Source == "Spatoloricarid sp.")
AllAzimuthStatistics(Spatoloricarid.ACSIVA$Azimuth)
AllModuleStatistics(Spatoloricarid.ACSIVA$Module)
```

*Supplemental Figure 1: Vector plots by species
```{r}
par(cex.axis=0.25)
par(cex.lab=0.25)

pdf(file = "Figure_ACSIVA.pdf", width = 20, height = 10)
par(mfrow=c(2,4))
radial.plot(c(0, Ancistrus.ACSIVA$Module), 
            c(0, Ancistrus.ACSIVA$radians), 
            lwd=1, line.col="#000000",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=TRUE, #put the concentric circle labels going down
            show.radial.grid=TRUE
)
radial.plot(c(0, Astroblepus.ACSIVA$Module), 
            c(0, Astroblepus.ACSIVA$radians), 
            lwd=1, line.col="#004949",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, Chaetostoma_brevae.ACSIVA$Module), 
            c(0, Chaetostoma_brevae.ACSIVA$radians), 
            lwd=1, line.col="#009292",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, Chaetostoma_microps.ACSIVA$Module), 
            c(0, Chaetostoma_microps.ACSIVA$radians), 
            lwd=1, line.col="#ff6db6",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, Cordylancistrus.ACSIVA$Module), 
            c(0, Cordylancistrus.ACSIVA$radians), 
            lwd=1, line.col="#ffb677",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, Hypostomus_niceforoi.ACSIVA$Module), 
            c(0, Hypostomus_niceforoi.ACSIVA$radians), 
            lwd=1, line.col="#490092",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, Lamontichthys.ACSIVA$Module), 
            c(0, Lamontichthys.ACSIVA$radians), 
            lwd=1, line.col="#006ddb",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
radial.plot(c(0, Spatoloricarid.ACSIVA$Module), 
            c(0, Spatoloricarid.ACSIVA$radians), 
            lwd=1, line.col="#b66dff",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=FALSE
)
dev.off()

#Plot mean of species
par(cex.axis=0.25)
par(cex.lab=0.25)

pdf(file = "Figure_ACSIVAmeans.pdf", width = 20, height = 10)
par(mfrow=c(2,4))
radial.plot(c(0, mean(Ancistrus.ACSIVA$Module)), 
            c(0, mean(Ancistrus.ACSIVA$radians)), 
            lwd=6, line.col="#000000",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=TRUE
)
radial.plot(c(0, mean(Astroblepus.ACSIVA$Module)), 
            c(0, mean(Astroblepus.ACSIVA$radians)), 
            lwd=6, line.col="#004949",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=TRUE
)
radial.plot(c(0, mean(Chaetostoma_brevae.ACSIVA$Module)), 
            c(0, mean(Chaetostoma_brevae.ACSIVA$radians)), 
            lwd=6, line.col="#009292",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=TRUE
)
radial.plot(c(0, mean(Chaetostoma_microps.ACSIVA$Module)), 
            c(0, mean(Chaetostoma_microps.ACSIVA$radians)), 
            lwd=6, line.col="#ff6db6",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=TRUE
)
radial.plot(c(0, mean(Cordylancistrus.ACSIVA$Module)), 
            c(0, mean(Cordylancistrus.ACSIVA$radians)), 
            lwd=6, line.col="#ffb677",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=TRUE
)
radial.plot(c(0, mean(Hypostomus_niceforoi.ACSIVA$Module)), 
            c(0, mean(Hypostomus_niceforoi.ACSIVA$radians)), 
            lwd=6, line.col="#490092",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=TRUE
)
radial.plot(c(0, mean(Lamontichthys.ACSIVA$Module)), 
            c(0, mean(Lamontichthys.ACSIVA$radians)), 
            lwd=6, line.col="#006ddb",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=TRUE
)
radial.plot(c(0, mean(Spatoloricarid.ACSIVA$Module)), 
            c(0, mean(Spatoloricarid.ACSIVA$radians)), 
            lwd=6, line.col="#b66dff",
            labels=NULL,
            radial.lim = c(0,3), #range of grid circle
            show.grid.label=FALSE, #put the concentric circle labels going down
            show.radial.grid=TRUE
)
dev.off()
```

*FIGURE 3: BaSIVA vs ACSIVA
```{r}
directionlabels=c("0", "90", "180", "270")

pdf(file = "BaSIVA.pdf", width = 4, height = 4)
            radial.plot(c(0, mean(Ancistrus$Module)), 
                        c(0, mean(Ancistrus$radians)), 
                        lwd=6, line.col="#000000", labels=directionlabels, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=TRUE)
                        
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Astroblepus$Module)), 
                        c(0, mean(Astroblepus$radians)), 
                        lwd=6, line.col="#004949", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                        
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Chaetostoma_brevae$Module)), 
                        c(0, mean(Chaetostoma_brevae$radians)), 
                        lwd=6, line.col="#009292", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                        
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Chaetostoma_microps$Module)), 
                        c(0, mean(Chaetostoma_microps$radians)), 
                        lwd=6, line.col="#ff6db6", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                        
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Cordylancistrus$Module)), 
                        c(0, mean(Cordylancistrus$radians)), 
                        lwd=6, line.col="#ffb677", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                        
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Hypostomus_niceforoi$Module)), 
                        c(0, mean(Hypostomus_niceforoi$radians)), 
                        lwd=6, line.col="#490092", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                        
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Lamontichthys$Module)), 
                        c(0, mean(Lamontichthys$radians)), 
                        lwd=6, line.col="#006ddb", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                        
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Spatoloricarid$Module)), 
                        c(0, mean(Spatoloricarid$radians)), 
                        lwd=6, line.col="#b66dff", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
dev.off()

pdf(file = "ACSIVA.pdf", width = 4, height = 4)
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Ancistrus.ACSIVA$Module)), 
                        c(0, mean(Ancistrus.ACSIVA$radians)), 
                        lwd=6, line.col="#000000", labels=directionlabels, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=TRUE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Astroblepus.ACSIVA$Module)), 
                        c(0, mean(Astroblepus.ACSIVA$radians)), 
                        lwd=6, line.col="#004949", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Chaetostoma_brevae.ACSIVA$Module)), 
                        c(0, mean(Chaetostoma_brevae.ACSIVA$radians)), 
                        lwd=6, line.col="#009292", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Chaetostoma_microps.ACSIVA$Module)), 
                        c(0, mean(Chaetostoma_microps.ACSIVA$radians)), 
                        lwd=6, line.col="#ff6db6", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Cordylancistrus.ACSIVA$Module)), 
                        c(0, mean(Cordylancistrus.ACSIVA$radians)), 
                        lwd=6, line.col="#ffb677", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Hypostomus_niceforoi.ACSIVA$Module)), 
                        c(0, mean(Hypostomus_niceforoi.ACSIVA$radians)), 
                        lwd=6, line.col="#490092", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Lamontichthys.ACSIVA$Module)), 
                        c(0, mean(Lamontichthys.ACSIVA$radians)), 
                        lwd=6, line.col="#006ddb", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Spatoloricarid.ACSIVA$Module)), 
                        c(0, mean(Spatoloricarid.ACSIVA$radians)), 
                        lwd=6, line.col="#b66dff", labels=NULL, radial.lim = c(0,10), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
dev.off()

pdf(file = "ACSIVAclose.pdf", width = 4, height = 4)
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Ancistrus.ACSIVA$Module)), 
                        c(0, mean(Ancistrus.ACSIVA$radians)), 
                        lwd=6, line.col="#000000", labels=directionlabels, radial.lim = c(0,3), show.grid.label=FALSE, show.radial.grid=TRUE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Astroblepus.ACSIVA$Module)), 
                        c(0, mean(Astroblepus.ACSIVA$radians)), 
                        lwd=6, line.col="#004949", labels=NULL, radial.lim = c(0,3), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Chaetostoma_brevae.ACSIVA$Module)), 
                        c(0, mean(Chaetostoma_brevae.ACSIVA$radians)), 
                        lwd=6, line.col="#009292", labels=NULL, radial.lim = c(0,3), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Chaetostoma_microps.ACSIVA$Module)), 
                        c(0, mean(Chaetostoma_microps.ACSIVA$radians)), 
                        lwd=6, line.col="#ff6db6", labels=NULL, radial.lim = c(0,3), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Cordylancistrus.ACSIVA$Module)), 
                        c(0, mean(Cordylancistrus.ACSIVA$radians)), 
                        lwd=6, line.col="#ffb677", labels=NULL, radial.lim = c(0,3), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Hypostomus_niceforoi.ACSIVA$Module)), 
                        c(0, mean(Hypostomus_niceforoi.ACSIVA$radians)), 
                        lwd=6, line.col="#490092", labels=NULL, radial.lim = c(0,3), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Lamontichthys.ACSIVA$Module)), 
                        c(0, mean(Lamontichthys.ACSIVA$radians)), 
                        lwd=6, line.col="#006ddb", labels=NULL, radial.lim = c(0,3), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
                  
            par(fig=c(0,1,0,1), new=TRUE)
            radial.plot(c(0, mean(Spatoloricarid.ACSIVA$Module)), 
                        c(0, mean(Spatoloricarid.ACSIVA$radians)), 
                        lwd=6, line.col="#b66dff", labels=NULL, radial.lim = c(0,3), show.grid.label=FALSE, show.radial.grid=FALSE, show.grid = FALSE)
dev.off()

spec.legend=unique(colblind_pal)

pdf(file = "legend.pdf",width = 4, height = 4)
plot.new()
legend(x="topleft",c("Ancistrus","Astroblepus","Chaetostoma brevae","Chaetostoma microps","Cordylancistrus","Hypostomus niceforoi","Lamontichthys","Spatoloricarid"), col = c("#000000","#004949","#009292","#ff6db6","#ffb677","#490092","#006ddb","#b66dff"), pch = 19)
dev.off()
```


Traditional trophic postions in tRophicPosition package
```{r}
si.data=read.csv('Raw_data.txt', header = T, sep = "\t")
si.data=subset(si.data, Source != "AUF-10519")
si.data=subset(si.data, Source != "AUF-10630")
si.data=subset(si.data, Source != "AUSI-10012_AUF-10498 (CHECK)")

si.data=si.data %>% mutate(Community = paste(Study,Location,"-",Source, sep = ""))

si.2BL=subset(si.data, Location != "15")
si.list <- extractIsotopeData(si.2BL, b1 = "plant_BL", b2 = "animal_BL", baselineColumn = "FG", consumersColumn = "Source", groupsColumn = "Location", d13C = "d13C", d15N = "d15N")

si.models=multiSpeciesTP(si.list, model = "twoBaselines")

sapply(si.models$"TPs", quantile, probs = c(0.025, 0.5, 0.975)) %>% round(3)

getPosteriorMode(si.models$"TPs")

pairwiseTP=pairwiseComparisons(si.models$TPs, print = TRUE)
pairwiseAlpha=pairwiseComparisons(si.models$Alphas, print = TRUE)
```

*Supplemental Figures 2-6: Vector plots by species
```{r}
pdf(file = "plots.pdf")
par(mfrow=c(4,5))
for (community in si.list) {plot(community)}
dev.off()

pdf(file = "trophicposition.pdf", width=10, height=6)
credibilityIntervals(si.models$df, x = "consumer", xlab ="Source", y1 = "median", y2 = "alpha.median")
dev.off()
```

Statisical analysis to determin if standardization significanly changed data: Yes
```{r}
d15stand=lm(final.vectors$d15N~final.vectors$standardized.d15N)
d13stand=lm(final.vectors$d13C~final.vectors$standardized.d13C)

summary(d15stand)
confint(d15stand)
summary(d13stand)
confint(d13stand)
```

## Map of localities
```{r}
locations=read.csv(file = "Map/LatLong.csv")
map=getMap(resolution = "high")
riversgeneral=readOGR("Map/Hydro/")
riversdetailed=readOGR("Map/hidro/")

pdf("EmbededMap.pdf", width = 6, height = 8)
par(fig = c(0,1,0,1))
plot(map, xlim = c(-83, -70), ylim = c(-18, 0),
     asp = 1, lwd=1,
     bg="lightblue", col="#ffffff")
plot(riversgeneral, col="lightblue", add=T, lwd=3)
map.axes()
points(x=locations$Long, y=locations$Lat, pch= 19, col="black", cex=1.5)

par(fig = c(0.08,.75, 0.06, .63), new = T)  
plot(map, xlim = c(-79.5, -78), ylim = c(-6, -5),
     asp = 1, lwd=1,
     bg="lightblue", col="#ffffff")
plot(riversdetailed, col="lightblue", add=T, lwd=2)
map.axes()
points(x=locations$Long, y=locations$Lat, pch= 19, col="black", cex=2)
dev.off()
```
